### 2013-03-26 doc/final_report/design.tex
Finished design chapter

The web frontend consists of sets of HTML and JavaScript interfaces that are
equipped to communicate with their relevant backend system using

@@

@@

@@

\subsubsection{Paper Upload Form}
Paper uploading is a

>>>>

The web frontend consists of sets of HTML and JavaScript interfaces that are
equipped to communicate with the backend systems discussed above using HTTP
requests. The most important aspect in designing the frontend was insuring that
the interfaces are intuitive and usable from the perspective of a non-technical
user. It was suggested that the system should look as similar as possible to
other online search and information retrieval systems in order to help users
who are already familiar with other systems in learning to use Partridge more
quickly.

@@

\begin{figure}[!htb]
\vspace{5mm}
\centering
\includegraphics[width=\textwidth]{images/design/query_mockup.png}
\caption{Mockup image for the Partridge Query Interface}
\label{fig:query_mockup}
\end{figure}

Figure \ref{fig:query_mockup} shows the initial design of the Partridge query
interface. The interface tries to make it easy for the user to both filter and
query papers in an intuitive way.

The filter interface on the left hand side of the query form allows the user to
use Partridge's machine learning classifiers to return subsets of the papers.
The selection box control in the top left of the form contains a list of each
of the types of paper within the database. The user should select one of these
types of paper to restrict their query to that type. There is also an ``All
Types" option in case they don't wish to use this filter.

The paper topic filtering system is displayed in the bottom left of the query
form. There is a `master list' of all paper topics in the corpus on the left
and a `query list' containing topics that the user wants to be included into
their search results on the right. The user selects items from each list and
can use the arrow buttons in between to move them depending on their query.

The search or `Keywords' section of the form shows a set of controls for
specifying terms that must appear within sections of a document for it to show
up in the search results. The user enters a search term in the input box on the
top right of the form and then selects which section of the paper the term
should appear within. This could be any of the CoreSC zones within the paper or
within the abstract. The user could also specify a specific author's name. Once
they are happy with their keywords and section, they click ``Add" and the
keyword/section pair are inserted into the table on the bottom right. If they
wish to remove a query constraint from this table, they can select it and click
the ``Delete" button.

Once the user is happy with their search, they can click the ``Search" button
at the extreme top right of the form to carry out the query and see the
results.

@@

Once a user has made their query, the results are displayed for them to peruse
and find relevant papers to read. Figure \ref{fig:results_mockup} shows a
mockup of the results view. This simplistic page lists all of the papers found
during the query in relevence order. The results are paginated so that the user
does not have to wait for a large page to render. It is hoped that users will
run specific queries that do not return a high number of results. There is a
prominent link at the top of the page that allows the user to go back to the
query form and amend their query if the results are not satisfactory.

\begin{figure}[!htb]
\vspace{5mm}
\centering
\includegraphics[width=\textwidth]{images/design/results_mockup.png}
\caption{Mockup image for the Partridge Search Results Interface}
\label{fig:results_mockup}
\end{figure}

Each paper is listed by title and author and the first few sentences of the
extract are also dislayed. The user can click on the paper title to be taken to
the Profile Page for that paper.

@@

The paper profile page is used to display all information about a specific
paper in the Partridge corpus to the user. A mockup of the Paper Profile page
can be seen in Figure \ref{fig:paper_profile}

\begin{figure}[!htb]
\vspace{5mm}
\centering
\includegraphics[width=\textwidth]{images/design/profile_mockup.png}
\caption{Mockup image for the Partridge Paper Profile Page}
\label{fig:paper_profile}
\end{figure}

The paper's title and author are displayed prominently in the top left hand
corner of the page. The full abstract text is shown so that the user can read
it and determine the paper's relevance to them. There is also a graph showing
each of the CoreSC types and proportion within the paper. If the user is
interested in the paper, they can click the Download link at the top of the
page to access the annotated XML file stored in the system.

\subsubsection{Paper Upload Form}
Paper uploading is another highly important user activity within Partridge.
Without users uploading papers, Partridge has no data to work with. It was
therefore, very important to make paper uploading as simplistic as possible to
the end user. Figure \ref{fig:paper_upload} shows Partridge's main paper upload
form.

\begin{figure}[!htb]
\vspace{5mm}
\centering
\includegraphics[width=\textwidth]{images/design/upload_mockup.png}
\caption{Mockup image for the Partridge Paper Upload Form}
\label{fig:paper_upload}
\end{figure}

The papers are selected using the familiar File Upload dialog used in any
website that requires users to upload files to the server. Multiple papers can
be selected for batch upload if required. Once the relevant papers are
selected, the user selects the Upload button to begin the process.

Once the upload process has started, the upload file browser and submit button
are disabled and a progress indicator as well as a text summary are displayed
directly underneath. Once the progress bar reaches 100\%, the upload file
browser becomes available again, or the user can navigate away from the page.

\section{ Summary}

All of Partridge's subsystems have carefully been designed in order to make
programming and implementing the project efficient and easy for the programmer.
The system architecture allows the implementation of modules independantly of
each other with minimal coupling and communication. Cohesion within the modules
is maximised, with related behaviours grouped together as far as possible.

The user interface has been designed to maximise usability for non-technical
users whilst effectively encoding the complicated nature of Partridge's
internal processes in a set of HTML forms.

Partridge has been developed using an iterative methodology and therefore some
of the designs descussed in this chapter have been modified during the
development of the project. However, these designs did provide an excellent
starting point for the implementation of the project.
